sensiAnPaper1All

### 2016-02-01 effectOfIndividualInputs.Rmd
exposure now taken from single random start val.

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #I could just rename one to exposure
  #BEWARE risk if future changes
  rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

>>>>

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #I could just rename one to exposure
  #BEWARE risk if future changes
  #1/2/16 don't need this now because I've saved exposure from the single original random value
  #rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"
